Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-07-29 paper/main.tex
include previously unused citation

We use principles from discrete differential geometry~\cite{bobenko2008discrete} to describe the
stiffness and flexibility of the bacterial rod.
As explained previously, MReB will counteract the bending of the rod, resulting in a stiffening
force.
In order to construct a model which can be parametrized and by method of Occam's Razor, we chose to
model the bacterium as a bending beam, thus utilizing the simplest solution which can still produce
the desired effects.
Such a beam can be represented by a collection of vertices $\vec{x}_i$ which are connected by a
springs of lengths $l_i$.
We use the notation $\vec{c}_i:=\vec{x}_i-\vec{x}_{i-1}$ with which the resulting force acting
between two vertices if given by

@@

%TODO use these citations
\cite{Chatterjee1988},\cite{Ursell2014}

>>>>

We use principles from discrete differential geometry~\cite{bobenko2008discrete} to describe the
stiffness and flexibility of the bacterial rod.
As explained previously, MReB will counteract the bending of the rod, resulting in a stiffening
force.
In principle, this stress will be dependent on the position inside the cell~\cite{Chatterjee1988}
but in order to construct a model which can be parametrized and by method of Occam's Razor, we chose
to model the bacterium as a bending beam, thus utilizing the simplest solution which can still
produce the desired effects.
Such a beam can be represented by a collection of vertices $\vec{x}_i$ which are connected by a
springs of lengths $l_i$.
We use the notation $\vec{c}_i:=\vec{x}_i-\vec{x}_{i-1}$ with which the resulting force acting
between two vertices if given by

@@
